Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-09 parallel.tex
Adding description of perfromance measurement implementation.

>>>>

\subsubsection{Performance Measurement \& Instrumentation \red{(Sam)}}

Because of the wide variety of simulations, methods, and uses of \bb{enzo}, it
is difficult to define exactly which routines are most costly during a given
simulation.  As such, we have designed a lightweight registering system that
has been implemented for the most commonly used routines (such as the
hydrodynamic and gravity solvers) as well as refinement level timers that
measure the (exclusive) time spent on each level.  Beyond this minimal set of
routines, we have designed a simple way for the user to modify the source
by adding TIMER_START(``Your Routine Name'') and TIMER_END(``Your Routine
Name'').  These timers are automatically registered in a
std::map\footnote{http://www.cplusplus.com/reference/map/map/}.  These timers
are created and managed individually on each processor in an asynchronous
fashion.

At each complete EvolveHierarchy (or less often if specified), each timer is
then communicated to the root processor where it calculates the mean, standard
deviation, minimum, and maximum for each of the timers across all processors. 
For level timers, there are also attributes such as the number of cell updates,
the current number of grids, and the average cells/s/MPI process.  This
information is then output to a ``performance.out'' logfile.  This provides a 
simplified interface to the user that can be used to diagnose performance 
issues as well as estimate a given problem type's scalability.  In addition to 
the logfile, we have developed a plotting interface for quickly producing 
figures that process the data from the logfile.  These capabilities are 
described in the online documentation, along with a further discussion of the 
performance measurement implementation.
